<span style="color:red;">*ANTs*</span><br> <small>_power tools for neuroimaging_</small>

### 2014-10-23 ants2015build.Rmd
ENH:  Add Bookstein review.
ENH:  More Bookstein.
ENH:  Adding more circularity material.

@@

@@

>>>>

## *ANTs* and the perils of circularity

@@

![](./philosophy/circularity/figures/voodoo.png)

![](./philosophy/circularity/figures/fastForward.png)

![](./philosophy/circularity/figures/tbss.png)

![](./philosophy/circularity/figures/antsFlavoredTbss1.png)

![](./philosophy/circularity/figures/antsFlavoredTbss2.png)

![](./philosophy/circularity/figures/antsFlavoredTbss3.png)

![](./philosophy/circularity/figures/antsFlavoredTbss4.png)

![](./philosophy/circularity/figures/antsFlavoredTbss5.png)

@@

![](./philosophy/circularity/figures/benefitsOfOpenScience.png)

## Command line help

<font size="5", color="lightgrey">
```
$ CreateDTICohort -h

COMMAND:
     CreateDTICohort

OPTIONS:
     -d, --image-dimensionality 2/3
     -a, --dti-atlas inputDTIAtlasFileName
     -x, --label-mask-image maskImageFileName
                            lowerThresholdFunction
     -n, --noise-sigma <noiseSigma=18>
     -p, --pathology label[<percentageChangeEig1=-0.05>,<percentageChangeAvgEig2andEig3=0.05>,<numberOfVoxels=all or percentageOfvoxels>]
     -w, --dwi-parameters [B0Image,directionFile,bvalue]
                          [B0Image,schemeFile]
     -r, --registered-population textFileWithFileNames.txt
     -o, --output [outputDirectory,fileNameSeriesRootName,<numberOfControls=10>,<numberOfExperimentals=10>]
     -h
     --help
```
</font>

## Which one is not warped?

![](./philosophy/circularity/figures/whichOneIsRegistered.png)

## _Answer_

![](./philosophy/circularity/figures/whichOneIsRegistered2.png)

![](./philosophy/circularity/figures/blobs1.png)

![](./philosophy/circularity/figures/blobs2.png)

![](./philosophy/circularity/figures/BooksteinReview1.png)
![](./philosophy/circularity/figures/BooksteinReview2.png)
![](./philosophy/circularity/figures/BooksteinReview3.png)
